---
title: "Mini Data-Analysis Deliverable 1"
output: github_document
---

# Welcome to your (maybe) first-ever data analysis project!

And hopefully the first of many. Let's get started:

1.  Install the [`datateachr`](https://github.com/UBC-MDS/datateachr) package by typing the following into your **R terminal**:

<!-- -->

    install.packages("devtools")
    devtools::install_github("UBC-MDS/datateachr")

2.  Load the packages below.

```{r}
library(datateachr)
library(tidyverse)
```

3.  Make a repository in the <https://github.com/stat545ubc-2022> Organization. You will be working with this repository for the entire data analysis project. You can either make it public, or make it private and add the TA's and Lucy as collaborators. A link to help you create a private repository is available on the #collaborative-project Slack channel. 

# Instructions

## For Both Milestones

-   Each milestone is worth 45 points. The number of points allocated to each task will be annotated within each deliverable. Tasks that are more challenging will often be allocated more points.

-   10 points will be allocated to the reproducibility, cleanliness, and coherence of the overall analysis. While the two milestones will be submitted as independent deliverables, the analysis itself is a continuum - think of it as two chapters to a story. Each chapter, or in this case, portion of your analysis, should be easily followed through by someone unfamiliar with the content. [Here](https://swcarpentry.github.io/r-novice-inflammation/06-best-practices-R/) is a good resource for what constitutes "good code". Learning good coding practices early in your career will save you hassle later on!

## For Milestone 1

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-1.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work below --->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to the mini-analysis GitHub repository you made earlier, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 45 points: 43 for your analysis, 1 point for having your Milestone 1 document knit error-free, and 1 point for tagging your release on Github.

# Learning Objectives

By the end of this milestone, you should:

-   Become familiar with your dataset of choosing
-   Select 4 questions that you would like to answer with your data
-   Generate a reproducible and clear report using R Markdown
-   Become familiar with manipulating and summarizing your data in tibbles using `dplyr`, with a research question in mind.

# Task 1: Choose your favorite dataset (10 points)

The `datateachr` package by Hayley Boyce and Jordan Bourak currently composed of 7 semi-tidy datasets for educational purposes. Here is a brief description of each dataset:

-   *apt_buildings*: Acquired courtesy of The City of Toronto's Open Data Portal. It currently has 3455 rows and 37 columns.

-   *building_permits*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 20680 rows and 14 columns.

-   *cancer_sample*: Acquired courtesy of UCI Machine Learning Repository. It currently has 569 rows and 32 columns.

-   *flow_sample*: Acquired courtesy of The Government of Canada's Historical Hydrometric Database. It currently has 218 rows and 7 columns.

-   *parking_meters*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 10032 rows and 22 columns.

-   *steam_games*: Acquired courtesy of Kaggle. It currently has 40833 rows and 21 columns.

-   *vancouver_trees*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 146611 rows and 20 columns.

**Things to keep in mind**

-   We hope that this project will serve as practice for carrying our your own *independent* data analysis. Remember to comment your code, be explicit about what you are doing, and write notes in this markdown document when you feel that context is required. As you advance in the project, prompts and hints to do this will be diminished - it'll be up to you!

-   Before choosing a dataset, you should always keep in mind **your goal**, or in other ways, *what you wish to achieve with this data*. This mini data-analysis project focuses on *data wrangling*, *tidying*, and *visualization*. In short, it's a way for you to get your feet wet with exploring data on your own.

And that is exactly the first thing that you will do!

1.1 Out of the 7 datasets available in the `datateachr` package, choose **4** that appeal to you based on their description. Write your choices below:

**Note**: We encourage you to use the ones in the `datateachr` package, but if you have a dataset that you'd really like to use, you can include it here. But, please check with a member of the teaching team to see whether the dataset is of appropriate complexity. Also, include a **brief** description of the dataset here to help the teaching team understand your data.

<!-------------------------- Start your work below ---------------------------->

1: BC_COVID_Case (Daily reported positive cases of COVID-19 linked with the date of reported case, health authority where the case was reported to, age cohort of the case (e.g., <10, 10-19, 20-29, unknown), and case sex (male, female, unknown))
2: 7
3: 6
4: 5

<!----------------------------------------------------------------------------->

1.2 One way to narrowing down your selection is to *explore* the datasets. Use your knowledge of dplyr to find out at least *3* attributes about each of these datasets (an attribute is something such as number of rows, variables, class type...). The goal here is to have an idea of *what the data looks like*.

*Hint:* This is one of those times when you should think about the cleanliness of your analysis. I added a single code chunk for you below, but do you want to use more than one? Would you like to write more comments outside of the code chunk?

<!-------------------------- Start your work below ---------------------------->

```{r}
### EXPLORE HERE ###
## First 6 rows of dataframe
head(BC_COVID_Cases)
head(vancouver_trees)
head(steam_games)
head(parking_meters)

## Last 6 rows of dataframe
tail(BC_COVID_Cases)
tail(vancouver_trees)
tail(steam_games)
tail(parking_meters)

## format of data
class(BC_COVID_Cases)
class(vancouver_trees)
class(steam_games)
class(parking_meters)

## dimension and data types within the dataframe (structure)
glimpse(BC_COVID_Cases)
glimpse(vancouver_trees)
glimpse(steam_games)
glimpse(parking_meters)
```

<!----------------------------------------------------------------------------->

1.3 Now that you've explored the 4 datasets that you were initially most interested in, let's narrow it down to 2. What lead you to choose these 2? Briefly explain your choices below, and feel free to include any code in your explanation.

<!-------------------------- Start your work below ---------------------------->

I will choose `BC_COVID_Cases` and `vancouver_trees`. `steam_games` has way too many columns consisting of solely character strings and the strings include very long descriptions of each name (e.g., columns such as `desc_snippet`, `recent_reviews`, `all_reviews`, `popular_tags`, `recommended_requirements`), which made difficult to perform quantitative analysis and graphing. Additionally, `parking_meters` has most columns comprised of solely prices at different time intervals, which would be difficult to explore their relationships (prices also in the character string format). However, for `BC_COVID_Cases`, I can look at the relationship between age group and case sex ratio. For `Vancouver_trees`, I can investigate the height and its relationship with different tree species (or the relationship between height and diameter). Therefore, I would rather choose the `BC_COVID_Cases` and `vancouver_trees` for my analysis due to higher significance and meaningfulness in exploring the relationships between factors of interests. 


<!----------------------------------------------------------------------------->

1.4 Time for the final decision! Going back to the beginning, it's important to have an *end goal* in mind. For example, if I had chosen the `titanic` dataset for my project, I might've wanted to explore the relationship between survival and other variables. Try to think of 1 research question that you would want to answer with each dataset. Note them down below, and make your final choice based on what seems more interesting to you!

If I had chosen the `vancouver_trees` dataset, I would explore the relationship between height and diameter.
If I had chosen the `parking_meters` dataset, I would explore the relationship between prices and the meter type.
If I had chosen the `steam_games` dataset, I would explore the relationship between genre and original price.
If I had chosen the `BC_COVID_Cases` dataset, I would explore the relationship between age group and case sex ratio.

I would choose the `vancouver_trees` dataset as it yields more interests to me.

<!-------------------------- Start your work below ---------------------------->

<!----------------------------------------------------------------------------->

# Important note

Read Tasks 2 and 3 *fully* before starting to complete either of them. Probably also a good point to grab a coffee to get ready for the fun part!

This project is semi-guided, but meant to be *independent*. For this reason, you will complete tasks 2 and 3 below (under the **START HERE** mark) as if you were writing your own exploratory data analysis report, and this guidance never existed! Feel free to add a brief introduction section to your project, format the document with markdown syntax as you deem appropriate, and structure the analysis as you deem appropriate. Remember, marks will be awarded for completion of the 4 tasks, but 10 points of the whole project are allocated to a reproducible and clean analysis. If you feel lost, you can find a sample data analysis [here](https://www.kaggle.com/headsortails/tidy-titarnic) to have a better idea. However, bear in mind that it is **just an example** and you will not be required to have that level of complexity in your project.

# Task 2: Exploring your dataset (15 points)

If we rewind and go back to the learning objectives, you'll see that by the end of this deliverable, you should have formulated *4* research questions about your data that you may want to answer during your project. However, it may be handy to do some more exploration on your dataset of choice before creating these questions - by looking at the data, you may get more ideas. **Before you start this task, read all instructions carefully until you reach START HERE under Task 3**.

2.1 Complete *4 out of the following 8 exercises* to dive deeper into your data. All datasets are different and therefore, not all of these tasks may make sense for your data - which is why you should only answer *4*. Use *dplyr* and *ggplot*.

1.  Plot the distribution of a numeric variable.
2.  Create a new variable based on other variables in your data (only if it makes sense)
3.  Investigate how many missing values there are per variable. Can you find a way to plot this?
4.  Explore the relationship between 2 variables in a plot.
5.  Filter observations in your data according to your own criteria. Think of what you'd like to explore - again, if this was the `titanic` dataset, I may want to narrow my search down to passengers born in a particular year...
6.  Use a boxplot to look at the frequency of different observations within a single variable. You can do this for more than one variable if you wish!
7.  Make a new tibble with a subset of your data, with variables and observations that you are interested in exploring.
8.  Use a density plot to explore any of your variables (that are suitable for this type of plot).

2.2 For each of the 4 exercises that you complete, provide a *brief explanation* of why you chose that exercise in relation to your data (in other words, why does it make sense to do that?), and sufficient comments for a reader to understand your reasoning and code.

<!-------------------------- Start your work below ---------------------------->

## Filter (subset) the observations (trees) to the years between 2000 and 2018
**We drop missing values for all variables except lats and longs since these two variables do not interfere with my scope of analysis.**
```{r}
vancouver_trees_2000_18 <- vancouver_trees %>% filter(between(date_planted, as.Date("2000-01-01"), as.Date("2018-12-31"))) %>% drop_na(-latitude, -longitude)
```

## Plot the distribution of tree diameter
```{r}
vancouver_trees_2000_18 %>% ggplot(aes(y = diameter)) + 
  geom_histogram() +
  ylim(0, 100)
```

## Explore the relationship between plant area and tree diameter
```{r}
vancouver_trees_2000_18 %>% 
  ggplot(aes(plant_area, diameter)) +
  geom_jitter(width = 0.1, alpha = 0.3) +
  ylim(0, 100) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 7))
```

## Use a boxplot to look at the frequency of tree diameters within different neighbourhoods
```{r}
vancouver_trees_2000_18 %>% 
  ggplot(aes(neighbourhood_name, diameter)) +
  geom_boxplot(width = 0.2) +
  ylim(0, 20) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 7))
```

## Use a density plot to explore diameters with curbings (yes/no) (Compare the diameter with curbing or not)
```{r}
vancouver_trees_2000_18 %>%
  ggplot(aes(diameter)) +
  geom_density(aes(color = curb)) +
  xlim(0, 100)
```


<!----------------------------------------------------------------------------->

# Task 3: Write your research questions (5 points)

So far, you have chosen a dataset and gotten familiar with it through exploring the data. Now it's time to figure out 4 research questions that you would like to answer with your data! Write the 4 questions and any additional comments at the end of this deliverable. These questions are not necessarily set in stone - TAs will review them and give you feedback; therefore, you may choose to pursue them as they are for the rest of the project, or make modifications!

<!--- *****START HERE***** --->

1. What is the relationship between tree diameters and curbing (yes/no)?
2. What is the relationship between height level and tree diameters?
3. Which neighbourhood has the highest "on average" tree diameters? How do the tree diameters differ across different neighbourhood?
4. Which height level contains the highest number of trees among which neighbourhood?

# Task 4: Process and summarize your data (13 points)

From Task 2, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions.

### 1.1 (10 points)

Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.

Ensure that the output of each operation is printed!

**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!
3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*
4.  Based on two categorical variables, calculate two summary statistics of your choosing.

**Graphing:**

5.  Create a graph out of summarized variables that has at least two geom layers.
6.  Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7.  Make a graph where it makes sense to customize the alpha transparency.
8.  Create 3 histograms out of summarized variables, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->

## RQ 1
```{r}
# Calculate the summary statistics (mean, range, median, IQR, and SD) for the diameters for both curbing and no curbing
RQ_1_mean <- vancouver_trees_2000_18 %>%
  group_by(curb) %>% 
  summarize(diameter_mean = mean(diameter, na.rm=T))

RQ_1_range <- vancouver_trees_2000_18 %>%
  group_by(curb) %>% 
  summarize(diameter_range = range(diameter, na.rm=T))

RQ_1_median <- vancouver_trees_2000_18 %>%
  group_by(curb) %>% 
  summarize(diameter_median = median(diameter, na.rm=T))

RQ_1_IQR <- vancouver_trees_2000_18 %>%
  group_by(curb) %>% 
  summarize(diameter_IQR = IQR(diameter, na.rm=T))

RQ_1_SD <- vancouver_trees_2000_18 %>%
  group_by(curb) %>% 
  summarize(diameter_SD = sd(diameter, na.rm=T))

# Kernel density plot for the tree diameters with curbing and no curbing
vancouver_trees_2000_18 %>%
  ggplot(aes(diameter)) +
  geom_density(aes(fill = curb), alpha = 0.75) +
  xlim(0, 20)
```

It slightly helps answering RQ 1 because from the statistical mean diameter for curbing (yes/no) and their kernel density distributions, we can infer that they are similar but the other summary statistics (e.g. range, IQR, SD) also provide more information in which no curbing has higher diameter range and SD meaning more spread out than with curbing. However, no curbing has lower IQR than with curbing. 

## RQ 2

```{r}
# Create a categorical variable (height_level) with 3 groups from an existing numerical variable (height_range_id)
height_class <- cut(vancouver_trees_2000_18$height_range_id,
                                            breaks=c(-Inf, 3, 6, Inf),
                                            labels=c('Low', 'Medium', 'high'))
vancouver_trees_2000_18$height_level <- factor(height_class)

# Boxplot for comparing the tree diameters across three levels of heights
vancouver_trees_2000_18 %>% 
  ggplot(aes(height_level, diameter)) +
  geom_boxplot(width = 0.2, size = 0.8, alpha = 0.5) +
  xlab("height level") +
  ylim(0,50)
```
It helps answer RQ2 since by looking at the boxplot, we can infer that roughly medium height trees have the highest "on average" diameters. However, to deduct if the differences in diameters between these three height levels are statistically significant, we need to use ANOVA to infer the relationship. The descriptive boxplot only gives a rough estimate of the relationship. 

## RQ 3

```{r}
# Calculate the summary statistics (mean, range, median, IQR, and SD) for the diameters for all neighbourhoods

RQ_3_summary <- vancouver_trees_2000_18 %>%
  group_by(neighbourhood_name) %>% 
  summarize(diameter_mean = mean(diameter, na.rm=T),
            diameter_range = range(diameter, na.rm=T),
            diameter_IQR = IQR(diameter, na.rm=T),
            diameter_SD = sd(diameter, na.rm=T),
            diameter_median = median(diameter, na.rm=T))

# Kernel density plot for the tree diameters across all neighbourhoods
vancouver_trees_2000_18 %>%
  ggplot(aes(diameter)) +
  geom_density(aes(fill = neighbourhood_name), alpha = 0.75) +
  xlim(0, 15)
```

The summary statistics give a comprehensive overview of the diameters across all neighbourhoods (like RQ1), but the kernel density plots here have too many neighbourhoods contained in which would lead to harder visualization (deviation from the focus); therefore, it is perhaps better to use other statistical analysis tools/methods to investigate how tree diameters differ across the neighbourhoods. Overall from this density plot, we can see almost no difference in the distribution of diameters across neighbourhoods. 


## RQ 4
```{r}
# Find the number of trees for each height level within each neighbourhood
RQ4 <- vancouver_trees_2000_18 %>% 
  group_by(neighbourhood_name, height_level) %>% 
  summarize(n = n())

# plot the number of trees for each height level for each neighbourhood (count in logarithmic)
vancouver_trees_2000_18 %>% ggplot(aes(neighbourhood_name, fill=height_level)) +
  geom_bar(position = "dodge") +
  scale_y_log10("Number of Trees (thousands)") +
  xlab("Neighbourhood") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 7)) 
```
It answers RQ 4 because we are investigating Which height level contains the highest number of trees among which neighbourhood and the side-by-side bar charts visually provides the information in which we can directly see their relationships. 


<!----------------------------------------------------------------------------->

### 1.2 (3 points)

Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?

From all research questions, these plots all give a rough and preliminary estimate of how the bivariate or perhaps multivariate relationships would look like. However, as discussed above, many of the visual representations only give a rough overview and I'm interested in detecting the statistical differences and relationships between these variables of interests and perhaps adding more complexity by using more statistical analysis methods could help. From the density plots for RQ1 and 3， there are almost no relationships between tree diameters and curbing, and tree diameters variations across neighbourhoods. I would say RQ2 provides the most interesting results as I always think higher height would be associated with larger diameters (hypothesis) and in reality, trees of medium height actually yields relatively largest diameter. 


<!-------------------------- Start your work below ---------------------------->

<!----------------------------------------------------------------------------->

### Attribution

Thanks to Icíar Fernández Boyano for mostly putting this together, and Vincenzo Coia for launching.







