---
title: "Mini Data Analysis Milestone 2"
output: github_document
---

*To complete this milestone, you can edit [this `.rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are commented out with `<!--- start your work here--->`. When you are done, make sure to knit to an `.md` file by changing the output in the YAML header to `github_document`, before submitting a tagged release on canvas.*

# Welcome to your second (and last) milestone in your mini data analysis project!

In Milestone 1, you explored your data, came up with research questions, and obtained some results by making summary tables and graphs. This time, we will first explore more in depth the concept of *tidy data.* Then, you'll be sharpening some of the results you obtained from your previous milestone by:

-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

**NOTE**: The main purpose of the mini data analysis is to integrate what you learn in class in an analysis. Although each milestone provides a framework for you to conduct your analysis, it's possible that you might find the instructions too rigid for your data set. If this is the case, you may deviate from the instructions -- just make sure you're demonstrating a wide range of tools and techniques taught in this class.

# Instructions

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work here--->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to your mini-analysis GitHub repository, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 55 points (compared to the 45 points of the Milestone 1): 45 for your analysis, and 10 for your entire mini-analysis GitHub repository. Details follow.

**Research Questions**: In Milestone 1, you chose two research questions to focus on. Wherever realistic, your work in this milestone should relate to these research questions whenever we ask for justification behind your work. In the case that some tasks in this milestone don't align well with one of your research questions, feel free to discuss your results in the context of a different research question.

# Learning Objectives

By the end of this milestone, you should:

-   Understand what *tidy* data is, and how to create it using `tidyr`.
-   Generate a reproducible and clear report using R Markdown.
-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

# Setup

Begin by loading your data and the tidyverse package below:

```{r, message = FALSE}
library(datateachr) # <- might contain the data you picked!
library(tidyverse)
library(lubridate)
library(broom)
```

# Task 1: Tidy your data (15 points)

In this task, we will do several exercises to reshape our data. The goal here is to understand how to do this reshaping with the `tidyr` package.

A reminder of the definition of *tidy* data:

-   Each row is an **observation**
-   Each column is a **variable**
-   Each cell is a **value**

*Tidy'ing* data is sometimes necessary because it can simplify computation. Other times it can be nice to organize data so that it can be easier to understand when read manually.

### 2.1 (2.5 points)

Based on the definition above, can you identify if your data is tidy or untidy? Go through all your columns, or if you have \>8 variables, just pick 8, and explain whether the data is untidy or tidy.

<!--------------------------- Start your work below --------------------------->

It is tidy because the the underlying variables are represented in columns and observations are represented in rows (each observation is a tree that has many attributes like tree_id across the columns, in which these attributes are basically variables that belong to each observation). And the values (cells) under different variable columns are of a specific data type (e.g., character string, numeric). Nothing is messy/untidy in terms of the data organization. 

I also specifically picked 8 variables:

* `root_barrier`, 
* `plant_area`, 
* `neighbourhood_name`,
* `street_side_name`,
* `height_range_id`, 
* `diameter`, 
* `curb`, 
* `date_planted`, 

```{r}
head(vancouver_trees)

vancouver_trees_eight_var <- vancouver_trees %>% 
  select(root_barrier,
         plant_area,
         neighbourhood_name,
         street_side_name,
         height_range_id,
         diameter,
         curb,
         date_planted,
         )
```

Based on the 8 variables, this data subset is also tidy because each row is an observation, each column is a variable, and each cell is a value.

<!----------------------------------------------------------------------------->

### 2.2 (5 points)

Now, if your data is tidy, untidy it! Then, tidy it back to it's original state.

If your data is untidy, then tidy it! Then, untidy it back to it's original state.

Be sure to explain your reasoning for this task. Show us the "before" and "after".

<!--------------------------- Start your work below --------------------------->

```{r}

head(vancouver_trees)

## Untidy (because data is tidy and clean) 
vancouver_trees_before <- vancouver_trees %>% 
                          drop_na(date_planted, longitude, latitude, diameter, height_range_id) %>%  
                          ## dropped all NA values within these columns/variables because they interfere with the                              ## scope of untidy here
                          separate(date_planted, into = c("Year", "Month", "Day"), sep = "-", remove = T) %>% 
                          separate(longitude, into = c("long_int", "long_dec"), sep = "\\.", remove = T) %>% 
                          separate(latitude, into = c("lat_int", "lat_dec"), sep = "\\.", remove = T) %>% 
                          pivot_longer(
                            cols = c(diameter, height_range_id),
                            names_to = "diameter_and_height",
                            values_to = "values") %>% 
                          pivot_longer(
                            cols = c(Year, Month, Day),
                            names_to = "time_type",
                            values_to = "time_values"
                            ) %>% 
                          pivot_longer(
                            cols = c(long_int, long_dec, lat_int, lat_dec),
                            names_to = "coordinate_sub",
                            values_to = "coordinate_number"
                            )

```

  The data looks very untidy (and unorganized) now as I first used `separate` function to separate the `date_planted` and `longitude` and `latitude` into separate columns (or variables) including the `Year`, `Month`, `Day`, `long_int`, `long_dec` (longitudes separated into the integers and decimals based on the dot), `lat_int`, `lat_dec` (same process as longitude separation). 
  
  I then used `pivot_longer` function to increase number of rows and decrease number of columns, resulting in less columns (less variables) and more rows (or observations). Specifically, I created a new column called `diameter_and_height` through this function, which is comprised of character string data including only names of `diameter` and `height_range_id`. There are two other new columns resulting from `Year`, `Month`, `Day`, `long_int`, `long_dec`, `lat_int`, `lat_dec` including `time_type` (including the `Year`, `Month`, `Day`), `coordinate_sub` (including `long_int`, `long_dec`, `lat_int`, `lat_dec`). 


```{r}
## Re-tidy
vancouver_trees_after <- vancouver_trees_before %>% 
                          pivot_wider(names_from = coordinate_sub,
                                      values_from = coordinate_number) %>% 
                          pivot_wider(names_from = time_type,
                                      values_from = time_values) %>% 
                          pivot_wider(names_from = diameter_and_height,
                                      values_from = values) %>% 
                          unite(col = date_planted, Year, Month, Day, sep = "-", remove = T) %>% 
                          unite(col = latitude, lat_int, lat_dec, sep = "-", remove = T) %>% 
                          unite(col = longitude, long_int, long_dec, sep = "-", remove = T)  

```


  To tidy back to the original dataset, we use `pivot_wider` to increase the number of columns (variables) and decrease number of rows (observations) turning the `Year`, `Month`, `Day`, `long_int`, `long_dec`, `lat_int`, `lat_dec`, `diameter` and `height_range_id` into individuals columns (which are originally observations within the columns). I also united columns of `Year`, `Month`, `Day` back to `date_planted` and columns of `long_int`, `long_dec`, `lat_int`, `lat_dec` back to `longitude` and `latitude` respectively (through the function of `unite`). 


<!----------------------------------------------------------------------------->

### 2.3 (7.5 points)

Now, you should be more familiar with your data, and also have made progress in answering your research questions. Based on your interest, and your analyses, pick 2 of the 4 research questions to continue your analysis in the next four tasks:

<!-------------------------- Start your work below ---------------------------->

1.  What is the relationship between height level and tree diameters for trees planted between 2000 and 2018?
2.  Which height level contains the highest number of trees among which neighbourhood for trees planted between 2000 and 2018?

<!----------------------------------------------------------------------------->

Explain your decision for choosing the above two research questions.

<!--------------------------- Start your work below --------------------------->

  Referring back to milestone 1, I designed these four research questions because I'm interested in detecting the statistical differences and relationships between these variables of interests and perhaps with more complexity by using more statistical analysis methods. From the density plots for RQ1 and 3 (in milestone 1)， there are almost no relationships between tree diameters and curbing, and tree diameters variations across neighbourhoods. I would say RQ2 (What is the relationship between height level and tree diameters) provides the most interesting results as I always think higher height would be associated with larger diameters (hypothesis) and in reality, trees of medium height actually yields relatively largest diameter. Additionally, RQ4 (Which height level contains the highest number of trees among which neighbourhood) is also interesting as it investigates the relationship between two categorical variables, in which from the side-by-side bar chart produced for RQ4 yields some interesting patterns as there are more variations in the frequency/number of trees in the category of "medium height" compared to "low height" across neighbourhoods. There are also significantly higher number of trees in the "low height" category compared to "medium height". I also want to investigate a wide range of relationships between variables of different types including the categorical versus numeric variables (RQ2) and two categorical variables (RQ4), in which different inferential statistical analysis methods (including ANOVA and chi-square) can be employed to investigate such relationships. 

<!----------------------------------------------------------------------------->

Now, try to choose a version of your data that you think will be appropriate to answer these 2 questions. Use between 4 and 8 functions that we've covered so far (i.e. by filtering, cleaning, tidy'ing, dropping irrelevant columns, etc.).

<!--------------------------- Start your work below --------------------------->


Filter (subset) the observations (trees) to the years planted between 2000 and 2018

```{r}
vancouver_trees_RQ2 <-  vancouver_trees %>% 
                        filter(between(date_planted, ymd("2000-01-01"), ymd("2018-12-31"))) %>%  
                        ## subset to year planted between 2000 and 2018
                        select(height_range_id, diameter) %>% 
                        ## only select columns of interests for my RQ
                        drop_na(height_range_id, diameter) %>% 
                        ## drop all missing values in these two columns of interests (found 0 for both actually)
                        ## We do not want to drop NA values of other columns since the other column NAs do not                               interfere with our scope of analysis
                        filter(diameter > 0) %>% 
                        ## Diameter cannot be 0 or lower
                        mutate(height_level = factor(case_when(height_range_id < 4~ "Low",
                                                               height_range_id < 7 ~ "Medium",
                                                               TRUE ~ "High"),
                                                     levels = c("Low", "Medium", "High"))) %>% 
                        ## recategorization - create a new column/variable "height_level" including "Low"                                    ## ("height_range_id" from 0-3), "Medium" (from 4-6), and "High" (from 7-9)
                        select(height_level, diameter) %>% 
                        ## Reselect but this time the height_level and diameter
                        group_by(height_level) %>% 
                        arrange(height_level, diameter) %>% 
                        ## Arrange the height_level and diameter from smallest to largest
                        rename("tree_diameter" = "diameter")
                        ## Rename diameter as tree_diameter

vancouver_trees_RQ4 <- vancouver_trees %>% 
                       filter(between(date_planted, ymd("2000-01-01"), ymd("2018-12-31"))) %>%  
                       ## subset to year planted between 2000 and 2018
                       select(neighbourhood_name, height_range_id) %>% 
                       ## only select columns of interests for my RQ
                       drop_na(neighbourhood_name, height_range_id) %>% 
                       ## drop all missing values in these columns of interests (found 0 for both actually)
                       ## We do not want to drop NA values of other columns since the other column NAs do not                               interfere with our scope of analysis
                       mutate(height_level = factor(case_when(height_range_id < 4~ "Low",
                                                              height_range_id < 7 ~ "Medium",
                                                              TRUE ~ "High"),
                                                    levels = c("Low", "Medium", "High"))) %>% 
                       ## recategorization - create a new column/variable "height_level" including "Low"                                    ## ("height_range_id" from 0-3), "Medium" (from 4-6), and "High" (from 7-9)
                       mutate(neighbourhood_name = as_factor(neighbourhood_name)) %>% 
                       ## change the data type of neighbourhood_name from character to factor
                       select(neighbourhood_name, height_level) %>% 
                       ## Reselect but this time the neighbourhood_name, height_level
                       group_by(neighbourhood_name, height_level) %>% 
                       summarize(n = n()) ## make a new column of tree numbers for each height_level for each neighbourhood_name
```



<!----------------------------------------------------------------------------->

# Task 2: Special Data Types (10)

For this exercise, you'll be choosing two of the three tasks below -- both tasks that you choose are worth 5 points each.

But first, tasks 1 and 2 below ask you to modify a plot you made in a previous milestone. The plot you choose should involve plotting across at least three groups (whether by facetting, or using an aesthetic like colour). Place this plot below (you're allowed to modify the plot if you'd like). If you don't have such a plot, you'll need to make one. Place the code for your plot below.

<!-------------------------- Start your work below ---------------------------->

**Plot code copied and modified from milestone 1**

```{r}

vancouver_trees_plot_data <- vancouver_trees %>% 
                    filter(between(date_planted, ymd("2000-01-01"), ymd("2018-12-31"))) %>%  
                    select(neighbourhood_name, height_range_id) %>% 
                    drop_na(neighbourhood_name, height_range_id) %>% 
                    mutate(height_level = factor(case_when(height_range_id < 4~ "Low",
                                                              height_range_id < 7 ~ "Medium",
                                                              TRUE ~ "High"),
                                                           levels = c("Low", "Medium", "High"))) %>% 
                    mutate(neighbourhood_name = as_factor(neighbourhood_name)) %>%
                    select(neighbourhood_name, height_level)

vancouver_trees_plot_data %>% ggplot(aes(neighbourhood_name, fill=height_level)) +
  geom_bar(position = "dodge") +
  scale_y_log10("Number of Trees (thousands)") +
  xlab("Neighbourhood") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 7)) 

```


<!----------------------------------------------------------------------------->

Now, choose two of the following tasks.

1.  Produce a new plot that reorders a factor in your original plot, using the `forcats` package (3 points). Then, in a sentence or two, briefly explain why you chose this ordering (1 point here for demonstrating understanding of the reordering, and 1 point for demonstrating some justification for the reordering, which could be subtle or speculative.)




2.  Produce a new plot that groups some factor levels together into an "other" category (or something similar), using the `forcats` package (3 points). Then, in a sentence or two, briefly explain why you chose this grouping (1 point here for demonstrating understanding of the grouping, and 1 point for demonstrating some justification for the grouping, which could be subtle or speculative.)




3.  If your data has some sort of time-based column like a date (but something more granular than just a year):

    1.  Make a new column that uses a function from the `lubridate` or `tsibble` package to modify your original time-based column. (3 points)

        -   Note that you might first have to *make* a time-based column using a function like `ymd()`, but this doesn't count.
        -   Examples of something you might do here: extract the day of the year from a date, or extract the weekday, or let 24 hours elapse on your dates.

    2.  Then, in a sentence or two, explain how your new column might be useful in exploring a research question. (1 point for demonstrating understanding of the function you used, and 1 point for your justification, which could be subtle or speculative).

        -   For example, you could say something like "Investigating the day of the week might be insightful because penguins don't work on weekends, and so may respond differently".

<!-------------------------- Start your work below ---------------------------->

**Task Number**: 1

```{r}
Q2_Task1 <- vancouver_trees_plot_data %>% 
  mutate(neighbourhood_name = fct_rev(fct_infreq(neighbourhood_name))) %>% 
  mutate(height_level = fct_rev(fct_infreq(height_level)))


Q2_Task1 %>% ggplot(aes(neighbourhood_name, fill=height_level)) +
  geom_bar(position = "dodge") +
  scale_y_log10("Number of Trees (thousands)") +
  xlab("Neighbourhood") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 7)) +
  scale_fill_discrete(name="Height Level")
  
```

  I chose this ordering as first `fct_infreq()` function orders the level in my variables `neighbourhood_name` & `height_level` by decreasing frequency, in which for `neighbourhood_name` the neighbourhood is re-ordered by the decreasing frequency/total number of trees (for each neighbourhood) and for `height_level` the height level is reordered by the number of trees in each height level for each neighbourhood (no. of trees decreasing across each height level). The second `fct_rev` function reverses the level of factors for both `neighbourhood_name` & `height_level` in which the trend is reversed as the it is in increasing frequency of (number of) trees for the height levels and also for the neighbourhoods. I did not use `fct_reorder()` despite the fact that it is also releveling or reordering the levels of factors according to increasing numeric values corresponding to the levels of factors. Here my dataset can only be reordered or relevelled according to frequency or number of rows (aka trees) and not by numeric values; therefore, `fct_reorder()` will not work here. 
  
  I chose `fct_infreq()` and `fct_rev` because I want to showcase first the neighbourhood in the order according to the numbers of trees in each neighbourhood (increasing trend) and second the height level of each neighbourhood in an increasing frequency of tree numbers (where the number of trees increases with the height level for each neighbourhood, in which the low height trees also account for the greatest number for each neighbourhood, followed by medium heights and finally high heights). This would help me to better visualize and understand the pattern for a descriptive analysis on the research question on "Which height level contains the highest number of trees among which neighbourhood for trees planted between 2000 and 2018?"
  

<!----------------------------------------------------------------------------->

<!-------------------------- Start your work below ---------------------------->

**Task Number**: 2

```{r}

Q2_Task2 <- vancouver_trees_plot_data %>% mutate(
                        neighbourhood_name = fct_collapse(neighbourhood_name, 
                        Westside_Van = c("FAIRVIEW", "MARPOLE", "WEST POINT GREY",                                                                            "DUNBAR-SOUTHLANDS", "KERRISDALE", "SHAUGHNESSY",                                                                    "ARBUTUS-RIDGE", "KITSILANO", "SOUTH CAMBIE",                                                                        "OAKRIDGE"),
                        East_Van = c("GRANDVIEW-WOODLAND", "HASTINGS-SUNRISE","KENSINGTON-CEDAR COTTAGE",                                                 "KILLARNEY", "STRATHCONA", "VICTORIA-FRASERVIEW",                                                                    "RENFREW-COLLINGWOOD", "SUNSET"),
                        Others = c("MOUNT PLEASANT", "RILEY PARK"),
                        ## Mount Pleasant and Riley Park straddle both East Vancouver and the West Side
                        Downtown_Van = c("WEST END", "DOWNTOWN")))

Q2_Task2 %>% ggplot(aes(neighbourhood_name, fill=height_level)) +
  geom_bar(position = "dodge") +
  scale_y_log10("Number of Trees (thousands)") +
  xlab("Neighbourhood") +
  theme(axis.text.x = element_text(angle = 0, vjust = 1, hjust=0.5, size = 9)) +
  scale_fill_discrete(name="Height Level") +
  scale_x_discrete(labels=c("Westside Vancouver", "East Vancouver", "Downtown", "Other Neighbourhoods"))


```

  I chose `fct_collapse()` to help with grouping as this function collapses or groups the specified factor levels into manually defined groups, in which I have defined and renamed as "Westside Vancouver", "East Vancouver", "Downtown" (including neighbourhoods of West End and Downtown) and others (including neighbourhoods of Mount Pleasant and Riley Park as they straddle both East Vancouver and the West Side so no specific category they can fall into apart from "Other Neighbourhoods"). 
  
  I intially wanted to use `fct_others()` but this function only allows me to preserve or drop factor levels of interests and group the remaining levels into new category called "others", which misaligned what I'm trying to do here is to regroup all Vancouver neighbourhoods into more broader categories or definitions (Westside, East Van, Downtown, others) based on their broader geographic locations. As a result, I want to use this new definition of grouping to help me visualize the vancouver trees patterns better through looking at a broader geographic view. 

<!----------------------------------------------------------------------------->

# Task 3: Modelling

## 2.0 (no points)

Pick a research question, and pick a variable of interest (we'll call it "Y") that's relevant to the research question. Indicate these.

<!-------------------------- Start your work below ---------------------------->

**Research Question**: What is the relationship between height level and tree diameters for trees planted between 2000 and 2018?

**Variable of interest**: Tree Diameter (tree_diameter)

<!----------------------------------------------------------------------------->

## 2.1 (5 points)

Fit a model or run a hypothesis test that provides insight on this variable with respect to the research question. Store the model object as a variable, and print its output to screen. We'll omit having to justify your choice, because we don't expect you to know about model specifics in STAT 545.

-   **Note**: It's OK if you don't know how these models/tests work. Here are some examples of things you can do here, but the sky's the limit.

    -   You could fit a model that makes predictions on Y using another variable, by using the `lm()` function.
    -   You could test whether the mean of Y equals 0 using `t.test()`, or maybe the mean across two groups are different using `t.test()`, or maybe the mean across multiple groups are different using `anova()` (you may have to pivot your data for the latter two).
    -   You could use `lm()` to test for significance of regression.

<!-------------------------- Start your work below ---------------------------->

```{r}
Task3_Q1 <- aov(tree_diameter~height_level, data = vancouver_trees_RQ2) ## Assuming equal variance by default

# 2nd method (assuming equal variance to be True)
# Task3_Q1_2nd <- oneway.test(tree_diameter~height_level, data = vancouver_trees_RQ2, var.equal=T)

print(Task3_Q1)
# print(Task3_Q1_2nd)
```

There are two ways to do the hypothesis testing and inferential analysis using ANOVA but for simplicity, we only show method 1 here.
<!----------------------------------------------------------------------------->

## 2.2 (5 points)

Produce something relevant from your fitted model: either predictions on Y, or a single value like a regression coefficient or a p-value.

-   Be sure to indicate in writing what you chose to produce.
-   Your code should either output a tibble (in which case you should indicate the column that contains the thing you're looking for), or the thing you're looking for itself.
-   Obtain your results using the `broom` package if possible. If your model is not compatible with the broom function you're needing, then you can obtain your results by some other means, but first indicate which broom function is not compatible.

<!-------------------------- Start your work below ---------------------------->

I want to produce a summary result table of the ANOVA model including the **F-statistics** and **p-value** indicating if the mean value of tree diameter between each group (aka three height levels) is (not) equal or significantly different. 

```{r}
## Use summary() to produce the model results including the F-statistics and p-value
summary(Task3_Q1)

## print() used for Task3_Q1_2nd already tells the model results including the F-statistics and p-value
## print(Task3_Q1_2nd)

## tidy() from broom package produced a tibble which also contains the model result that we want (F-statistics and p-value) which are the same as generated by the previous two non-broom functions. 
tidy(Task3_Q1)
```

Based on `tidy(Task3_Q1)`, we can state that the mean value of tree diameter between "low height", "medium height", and "high height" is significantly different from each other (therefore not equal) with a F-statsitics of 3935.5 inferred by the very low p-value (p < 0.05)!

<!----------------------------------------------------------------------------->

# Task 4: Reading and writing data

Get set up for this exercise by making a folder called `output` in the top level of your project folder / repository. You'll be saving things there.

## 3.1 (5 points)

Take a summary table that you made from Milestone 1 (Task 4.2), and write it as a csv file in your `output` folder. Use the `here::here()` function.

-   **Robustness criteria**: You should be able to move your Mini Project repository / project folder to some other location on your computer, or move this very Rmd file to another location within your project repository / folder, and your code should still work.
-   **Reproducibility criteria**: You should be able to delete the csv file, and remake it simply by knitting this Rmd file.

<!-------------------------- Start your work below ---------------------------->

```{r}
### Summary Table from Milestone 1 (RQ4 summary table)

vancouver_trees_2000_18 <- vancouver_trees %>% filter(between(date_planted, as.Date("2000-01-01"), as.Date("2018-12-31"))) %>% drop_na(-latitude, -longitude)

height_class <- cut(vancouver_trees_2000_18$height_range_id,
                                            breaks=c(-Inf, 3, 6, Inf),
                                            labels=c('Low', 'Medium', 'high'))
vancouver_trees_2000_18$height_level <- factor(height_class)


RQ4 <- vancouver_trees_2000_18 %>% 
  group_by(neighbourhood_name, height_level) %>% 
  summarize(n = n())

here::here()

dir.create(here::here("output"))

write_csv(RQ4,
         here::here(
         "output",
         "neighbourhood_height_level_tree.csv"))

# show the directory location of "neighbourhood_height_level_tree.csv"
# dir(here::here("output"))

```


<!----------------------------------------------------------------------------->

## 3.2 (5 points)

Write your model object from Task 3 to an R binary file (an RDS), and load it again. Be sure to save the binary file in your `output` folder. Use the functions `saveRDS()` and `readRDS()`.

-   The same robustness and reproducibility criteria as in 3.1 apply here.

<!-------------------------- Start your work below ---------------------------->

```{r}

saveRDS(Task3_Q1,
         here::here(
         "output",
         "height_level_diameter_ANOVA_model"))

readRDS(here::here(
         "output",
         "height_level_diameter_ANOVA_model"))


```
<!----------------------------------------------------------------------------->

# Tidy Repository

Now that this is your last milestone, your entire project repository should be organized. Here are the criteria we're looking for.

## Main README (3 points)

There should be a file named `README.md` at the top level of your repository. Its contents should automatically appear when you visit the repository on GitHub.

Minimum contents of the README file:

-   In a sentence or two, explains what this repository is, so that future-you or someone else stumbling on your repository can be oriented to the repository.
-   In a sentence or two (or more??), briefly explains how to engage with the repository. You can assume the person reading knows the material from STAT 545A. Basically, if a visitor to your repository wants to explore your project, what should they know?

Once you get in the habit of making README files, and seeing more README files in other projects, you'll wonder how you ever got by without them! They are tremendously helpful.

## File and Folder structure (3 points)

You should have at least three folders in the top level of your repository: one for each milestone, and one output folder. If there are any other folders, these are explained in the main README.

Each milestone document is contained in its respective folder, and nowhere else.

Every level-1 folder (that is, the ones stored in the top level, like "Milestone1" and "output") has a `README` file, explaining in a sentence or two what is in the folder, in plain language (it's enough to say something like "This folder contains the source for Milestone 1").

## Output (2 points)

All output is recent and relevant:

-   All Rmd files have been `knit`ted to their output, and all data files saved from Task 4 above appear in the `output` folder.
-   All of these output files are up-to-date -- that is, they haven't fallen behind after the source (Rmd) files have been updated.
-   There should be no relic output files. For example, if you were knitting an Rmd to html, but then changed the output to be only a markdown file, then the html file is a relic and should be deleted.

Our recommendation: delete all output files, and re-knit each milestone's Rmd file, so that everything is up to date and relevant.

PS: there's a way where you can run all project code using a single command, instead of clicking "knit" three times. More on this in STAT 545B!

## Error-free code (1 point)

This Milestone 1 document knits error-free, and the Milestone 2 document knits error-free.

Plots failing to show up on Github in the .md counts as an error here. So does the entire .md failing to show up on Github in the .md ("Sorry about that, but we can't show files that are this big right now").

## Tagged release (1 point)

You've tagged a release for Milestone 1, and you've tagged a release for Milestone 2.

### Attribution

Thanks to Victor Yuan for mostly putting this together.
